Simulation of Congenital Heart Defect Corrective Surgeries Using Thin Shell Elements

### 2012-03-01 Doc/Miccai/shell-model.tex
Improved 2. section.
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@378 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

In congenital heart defect (CHD) corrective surgeries blood vessels respond to plastic interventions with a certain amount of deformation. Surgeons try to find an optimal approach to correct defects with a minimum of deformations and collisions that would have unnecessary negative impact on blood flow or that may lead to problems during growth of the patient. To be able to predict results for different surgical approaches a physicaly approriate model of blood vessels is mandatory. Furthermore, computation time of simulations must be low enough to enable interactive and usable planning software.

@@

\tomas{I'm adding this back, the previous focuess only on physical correctnes.}
Apart from physical accuracy the model should provide 
(I) a good support for the deformations by bending and twisting,
(II) an accurate modeling of the wall motion when the vessel is cut along its axis,
(III) global deformations of stitched vessels that capture their final configuration, after surgery,
(IV) collision response when detected (e.g. between the aortic arch and pulmonary artery).
All these requirements are fullfilled by the shell element model.

>>>>

In CHD corrective surgeries blood vessels respond to plastic interventions with a certain amount of deformation. Surgeons try to find an optimal approach to correct defects with a minimum of deformations and collisions that would have unnecessary negative impact on blood flow or that may lead to problems during growth of the patient. To be able to predict results for different surgical approaches a physicaly approriate model of blood vessels is mandatory. Furthermore, computation time of simulations must be low enough to enable interactive and usable planning software.

@@
